% SPDX-License-Identifier: GPL-2.0
% X-SPDX-Copyright-Text: (c) Solarflare Communications Inc

The information disclosed to you hereunder (the “Materials”) is provided 
solely for the selection and use of Xilinx products. To the maximum extent 
permitted by applicable law: (1) Materials are made available "AS IS" and 
with all faults, Xilinx hereby DISCLAIMS ALL WARRANTIES AND CONDITIONS, 
EXPRESS, IMPLIED, OR STATUTORY, INCLUDING BUT NOT LIMITED TO WARRANTIES OF 
MERCHANTABILITY, NON-INFRINGEMENT, OR FITNESS FOR ANY PARTICULAR PURPOSE; and 
(2) Xilinx shall not be liable (whether in contract or tort, including 
negligence, or under any other theory of liability) for any loss or damage of 
any kind or nature related to, arising under, or in connection with, the 
Materials (including your use of the Materials), including for any direct, 
indirect, special, incidental, or consequential loss or damage (including 
loss of data, profits, goodwill, or any type of loss or damage suffered as a 
result of any action brought by a third party) even if such damage or loss 
was reasonably foreseeable or Xilinx had been advised of the possibility of 
the same. Xilinx assumes no obligation to correct any errors contained in the 
Materials or to notify you of updates to the Materials or to product 
specifications. You may not reproduce, modify, distribute, or publicly 
display the Materials without prior written consent. Certain products are 
subject to the terms and conditions of Xilinx’s limited warranty, please 
refer to Xilinx’s Terms of Sale which can be viewed at 
\href{https://www.xilinx.com/legal.htm\#tos}{https://www.xilinx.com/legal.htm\#tos}; 
IP cores may be subject to warranty and support terms contained in a license 
issued to you by Xilinx. Xilinx products are not designed or intended to be 
fail-safe or for use in any application requiring fail-safe performance; you 
assume sole risk and liability for use of Xilinx products in such critical 
applications, please refer to Xilinx’s Terms of Sale which can be viewed at 
\href{https://www.xilinx.com/legal.htm\#tos}{https://www.xilinx.com/legal.htm\#tos}.

Onload is licensed under the GNU General Public License (Version 2, June
1991). See the LICENSE file in the distribution for details. The Onload
Extensions Stub Library is Copyright licensed under the BSD 2-Clause
License.

You will not disclose to a third party the results of any performance
tests carried out using Onload, Cloud Onload  or EnterpriseOnload without the 
prior written consent of Xilinx, Inc.

A list of patents associated with this product is at 
\href{http://www.solarflare.com/patent}{http://www.solarflare.com/patent}.

{\bfseries AUTOMOTIVE APPLICATIONS DISCLAIMER}

AUTOMOTIVE PRODUCTS (IDENTIFIED AS “XA” IN THE PART NUMBER) ARE NOT WARRANTED 
FOR USE IN THE DEPLOYMENT OF AIRBAGS OR FOR USE IN APPLICATIONS THAT AFFECT 
CONTROL OF A VEHICLE (“SAFETY APPLICATION”) UNLESS THERE IS A SAFETY CONCEPT 
OR REDUNDANCY FEATURE CONSISTENT WITH THE ISO 26262 AUTOMOTIVE SAFETY 
STANDARD (“SAFETY DESIGN”). CUSTOMER SHALL, PRIOR TO USING OR DISTRIBUTING 
ANY SYSTEMS THAT INCORPORATE PRODUCTS, THOROUGHLY TEST SUCH SYSTEMS FOR 
SAFETY PURPOSES. USE OF PRODUCTS IN A SAFETY APPLICATION WITHOUT A SAFETY 
DESIGN IS FULLY AT THE RISK OF CUSTOMER, SUBJECT ONLY TO APPLICABLE LAWS AND 
REGULATIONS GOVERNING LIMITATIONS ON PRODUCT LIABILITY.

{\bfseries Copyright}

© Copyright \the\year{} Xilinx, Inc. Xilinx, the Xilinx logo, Solarflare, 
Onload, TCPDirect, and other designated brands included herein are trademarks 
of Xilinx in the United States and other countries. All other trademarks are 
the property of their respective owners.
